Understanding the Impact of Socioeconomic and Regional Factors on Health and Educational Outcomes

### 2024-12-15 paper.qmd
fixed rendered photo
fixing format
other files
final

```{r, echo= FALSE, warning = FALSE, message=FALSE}
library("dplyr") 
library(mice) 
library(sjlabelled) 
library(tidyverse) 
library("modelsummary") 
library(car)
library(GGally)
library(ggplot2)
library(patchwork)
library(caret)
library(pROC)
library(pander)
library(kableExtra)
```

@@

Table 3 below displays the odds ratio results from the logistic regression model for school funding adequacy, with the South as the baseline category for the categorical region variable. While all estimates are statistically significant at the 0.05 significance level, exponentiated regression coefficient estimates from the logistic model demonstrate that the level of residential segregation, the median household income, and median property tax of the county have very minimal impacts on the odds of a school being adequately funded.

@@

```{r}
renamed_data <- completed_data %>%
  rename(
    "Residential Segregation" = Residential.Segregation.Index,
    "Median Household Income" = Median.Household.Income,
    "Median Property Tax" = Median.Prop.Tax,
    "School Funding Adequacy" = School.Funding.Adequacy, 
    "Life Expectancy" = Life.Expectancy,
    "% Limited Access, Healthy Foods" = X..Limited.Access.to.Healthy.Foods,
    "% Uninsured Adults" = X..Uninsured.Adults,
    "Region" = Region_fac,
    "School Funding Binary" =School.Funding.Cat)

@@

```{r, include=FALSE, echo=FALSE}
summary(completed_data)
```

>>>>

```{r, echo= FALSE, warning = FALSE, message=FALSE}
library("dplyr") 
library(mice) 
library(sjlabelled) 
library(tidyverse) 
library("modelsummary") 
library(car)
library(GGally)
library(ggplot2)
library(patchwork)
library(caret)
library(pROC)
library(pander)
```

@@

Table 3 below displays the odds ratio results from the logistic regression model for school funding adequacy, with the South as the baseline category for the categorical region variable. While all estimates are statistically significant at the 0.05 significance level, exponentiated regression coefficients from the logistic model demonstrate median household income and median property tax of the county have almost no impact on the odds of a school being adequately funded. Our results demonstrate that a one unit increase to the residential segregation index increases the odds of school funding adequacy by 0.02 times, allowing us to conclude that residential segregation has a minimal effect on the odds of the school being adequately funded. Figure 2 demonstrates an interesting trend–each region shows a different relationship between the residential segregation distribution of adequately and inadequately funded schools, pointing to a potential interaction between region and segregation.

@@

```{r, include=FALSE, echo=FALSE}
renamed_data <- completed_data %>%
  rename(
    "Residential Segregation" = Residential.Segregation.Index,
    "Median Household Income" = Median.Household.Income,
    "Median Property Tax" = Median.Prop.Tax,
    "School Funding Adequacy" = School.Funding.Adequacy, 
    "Life Expectancy" = Life.Expectancy,
    "% Limited Access, Healthy Foods" = X..Limited.Access.to.Healthy.Foods,
    "% Uninsured Adults" = X..Uninsured.Adults,
    "Region" = Region_fac,
    "School Funding Binary" =School.Funding.Cat)

@@

## ![](images/clipboard-2912764107.png)
